A novel approach to the theme for syntax highlighting selection based on Color Correlated Temperature in terms of blue light hazard

### 2022-04-21 doc/manuscript.tex
.

\documentclass{article}
\usepackage{hyperref}
\usepackage{ifthen, array, booktabs}
\usepackage{csvsimple}
\usepackage{float}
\usepackage{verbatimbox}
\usepackage{fancyvrb}
\usepackage{amsmath}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}
\usepackage{comment}
\usepackage{svg}
\svgpath{{./img/}}
\usepackage{pgfplots}
\pgfplotsset{compat=1.17}

@@

\begin{figure}[h]
  \begin{tikzpicture}
    \begin{axis}[
      xbar,
      tick label style={font=\footnotesize},
      ytick={1,2,3,4,5,6,7,8},
      yticklabels={Visual Studio C/C++,Winter is Coming,Monokai Pro,Night Owl,Nord,Tokyo Night,Gruvbox,Github},
      xticklabel style={
        /pgf/number format/fixed,
        /pgf/number format/precision=5
      },
      scaled x ticks=false,
      xlabel=$CCT (K)$,
      y=12mm,
    ]
    \addplot coordinates {
      (8406,1)  % Visual C/C++ dark
      (16945,2) % Winter is Coming dark
      (2509,3)  % Monokai Pro dark
      (15011,4) % Night Owl dark
      (3667,5)  % Nord dark
      (19253,6) % Tokyo Night dark
      (1675,7)  % Gruvbox dark
      (9842,8)  % Github dark
    };
    \addplot coordinates {
      (8824,1)  % Visual C/C++ light
      (33440,2) % Winter is Coming light
      (2894,3)  % Monokai Pro light
      (30055,4) % Night Owl light
      (7837,5)  % Nord light
      (19322,6) % Tokyo Night light
      (2976,7)  % Gruvbox light
      (12887,8) % Github light
    };
    \legend {Dark, Light};
    \draw[thick,dashed] (axis cs: 6500,0) -- (axis cs: 6500,8.5) node[anchor=east]{D65};
    \end{axis}
  \end{tikzpicture}
  \caption{Dark-Light CCT value comparison of themes in pairs}
  \label{fig:dark-light-pair-compare}
\end{figure}

@@

\begin{figure}[h]
  \begin{tikzpicture}
    \begin{axis}[
      xbar,
      tick label style={font=\footnotesize},
      ytick={1,2,3,4,5,6,7,8,9},
      yticklabels={One Dark,Github,Dracula Official,Atom One Dark,One Monokai,Shades of Purple,Palenight,Andromeda,Plastic},
      xticklabel style={
        font=\tiny,
        /pgf/number format/fixed,
        /pgf/number format/precision=5
      },
      scaled x ticks=false,
      xlabel=$CCT (K)$,
    ]
    \addplot coordinates {
      (10613,1) % One Dark
      (9842,2)  % Github
      (6532,3)  % Dracula Official
      (10613,4) % Atom One Dark
      (3923,5)  % One Monokai
      (10488,6) % Shades of Purple
      (16669,7) % Palenight
      (2191,8)  % Andromeda
      (9720,9)  % Plastic
    };
    \draw[thick,dashed] (axis cs: 6500,0) -- (axis cs: 6500,9.5) node[anchor=east, yshift=-8.5mm]{D65};
    \end{axis}
  \end{tikzpicture}
  \caption{CCT value comparison of dark themes}
  \label{fig:dark-compare}
\end{figure}

>>>>

\documentclass{article}
\usepackage{hyperref}
\usepackage{ifthen, array, booktabs}
\usepackage{csvsimple}
\usepackage{float}
\usepackage{verbatimbox}
\usepackage{fancyvrb}
\usepackage{amsmath}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}
\usepackage{comment}
\usepackage{svg}
\svgpath{{./img/}}
\usepackage{pgfplots, pgfplotstable}
\pgfplotsset{compat=1.17}

@@

\pgfplotstableread[col sep=comma,text indicator="]{./data/themes-dual.csv}\dualtable
\pgfplotstabletranspose[colnames from=themes]\tabledual{\dualtable}

\begin{figure}[h]
  \begin{tikzpicture}
    \begin{axis}[
      xbar,
      tick label style={font=\footnotesize},
      ytick=data,
      yticklabels from table={\tabledual}{colnames},
      xticklabel style={
        /pgf/number format/fixed,
        /pgf/number format/precision=5
      },
      scaled x ticks=false,
      xlabel=$CCT (K)$,
      y=12mm,
    ]
      \addplot table[x=dark,y=index] {\tabledual};
      \addplot table[x=light,y=index] {\tabledual};
      \legend {Dark, Light};
      \draw[thick,dashed] (axis cs: 6500,0) -- (axis cs: 6500,8.5) node[anchor=east]{D65};
    \end{axis}
  \end{tikzpicture}
  \caption{Dark-Light CCT value comparison of themes in pairs}
  \label{fig:dark-light-pair-compare}
\end{figure}

@@

\pgfplotstableread[col sep=comma,text indicator="]{./data/themes-dark.csv}\darktable
\pgfplotstabletranspose[colnames from=themes]\tabledark{\darktable}

\begin{figure}[h]
  \begin{tikzpicture}
    \begin{axis}[
      xbar,
      tick label style={font=\footnotesize},
      ytick=data,
      yticklabels from table={\tabledark}{colnames},
      xticklabel style={
        /pgf/number format/fixed,
        /pgf/number format/precision=5
      },
      scaled x ticks=false,
      xlabel=$CCT (K)$,
      xmin=5000,
      y=12mm,
    ]
      \addplot table[x=ccts,y=index] {\tabledark};
      \draw[thick,dashed] (axis cs: 6500,0) -- (axis cs: 6500,8.5) node[anchor=east, yshift=-7.5mm]{D65};
    \end{axis}
  \end{tikzpicture}
  \caption{CCT value comparison of dark themes}
  \label{fig:dark-compare}
\end{figure}
